Staged Abstract Interpreters

### 2019-09-11 paper/50_stageabs.tex
misc

The @close@ method now is a mix of the \textit{staged} concrete version and
unstaged \textit{abstract} version. We first build a current-stage function @f@, which
takes four next-stage values, including the argument and latest store, and
@in/out@ caches additionally. Inside of @f@, we collapse the monadic value of
type @Ans@ to grounded values of type @Result@, by providing the desired
arguments, i.e., the new environment, new store, and two caches. The collapsing
of monadic values happens at the current-stage, so the invocation of @ev@ is unfolded
within staging. Finally, we generate a singleton set containing the compiled
next-stage closure (@emit_compiled_clo@), which is represented by an IR node
in LMS.
\begin{lstlisting}
  def emit_compiled_clo(f: (Rep[Value], Rep[Store], Rep[Cache], Rep[Cache])
                           => Rep[(Set[(Value,Store)], Cache)], λ: Lam, ρ: Exp[Env]): Rep[AbsValue]
  def close(ev: Expr => Ans)(λ: Lam, ρ: Rep[Env]): Rep[Value] = {
    val Lam(x, e) = λ
    val f: (Rep[Value],Rep[Store],Rep[Cache],Rep[Cache]) => Rep[(Set[(Value,Store)],Cache)] = {
      case (arg, σ, in, out) =>
        val α = alloc(σ, x)
        ev(e)(ρ + (unit(x) → α))(σ ⊔ Map(α → arg))(in)(out)
    }; Set[AbsValue](emit_compiled_clo(f, λ, ρ)) }
\end{lstlisting}

>>>>

The @close@ method now is a mix of the \textit{staged} concrete version and
unstaged \textit{abstract} version. We first build a current-stage function @f@, which
takes four next-stage values, including the argument and latest store, and
@in/out@ caches additionally. Inside @f@, we collapse the monadic value of
type @Ans@ to grounded values of type @Result@, by providing the desired
arguments, i.e., the new environment, new store, and two caches. The collapsing
of monadic values happens at the current-stage, so the invocation of @ev@ is unfolded
within staging. Finally, we generate a singleton set containing the compiled
next-stage closure (@emit_compiled_clo@), which is represented by an IR node
in LMS.
\begin{lstlisting}
  def emit_compiled_clo(f: (Rep[Value], Rep[Store], Rep[Cache], Rep[Cache])
                           => Rep[(Set[(Value,Store)], Cache)], λ: Lam, ρ: Exp[Env]): Rep[AbsValue]
  def close(ev: Expr => Ans)(λ: Lam, ρ: Rep[Env]): Rep[Value] = {
    val Lam(x, e) = λ
    val f: (Rep[Value],Rep[Store],Rep[Cache],Rep[Cache]) => Rep[(Set[(Value,Store)],Cache)] = {
      case (arg, σ, in, out) =>
        val α = alloc(σ, x)
        ev(e)(ρ + (unit(x) → α))(σ ⊔ Map(α → arg))(in)(out)
    }; Set[AbsValue](emit_compiled_clo(f, λ, ρ)) }
\end{lstlisting}
